---
title: "Capstone"
author: "JP Pugliese"
date: "11/20/2019"
output:
  word_document:
    toc: yes
    toc_depth: '2'
  pdf_document:
    highlight: pygments
    keep_tex: yes
    number_sections: yes
    toc: yes
    toc_depth: 2
  html_document: default
abstract: This is the final assignment for the Harvard Data Science Professional course.  The
  chosen project is using the Kickstarter Kaggle dataset and apply machine learning
  to estimate the success of a campaign.
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Executive Summary

Using the most recent dataset in Kaggle for the different projects having run on Kickstarter, we look at the data structure, visualizing different trends.  Some data cleansing was required to apply some machine learning models in order to forecast any likelihood of a campaign success in Kickstarter.

```{r ,include=FALSE, echo=FALSE}
# Install all needed libraries if it is not present
if(!require(tidyverse)) install.packages("tidyverse")
if(!require(kableExtra)) install.packages("kableExtra")
if(!require(tidyr)) install.packages("tidyr")
if(!require(tidyverse)) install.packages("tidyverse")
if(!require(stringr)) install.packages("stringr")
if(!require(ggplot2)) install.packages("ggplot2")
if(!require(gbm)) install.packages("gbm")
if(!require(dplyr)) install.packages("dplyr")
if(!require(caret)) install.packages("caret")
if(!require(xgboost)) install.packages("xgboost")
if(!require(e1071)) install.packages("e1071")
if(!require(class)) install.packages("class")
if(!require(ROCR)) install.packages("ROCR")
if(!require(randomForest)) install.packages("randomForest")
if(!require(PRROC)) install.packages("PRROC")
if(!require(reshape2)) install.packages("reshape2")
if(!require(knitr)) install.packages("knitr")
if(!require(ggthemes)) install.packages("ggthemes")
if(!require(lubridate)) install.packages("lubridate")
if(!require(pROC)) install.packages("pROC")
if(!require(rpart)) install.packages("rpart")
if(!require(rpart.plot)) install.packages("rpart.plot")
if(!require(tree)) install.packages("tree")

# Loading all needed libraries
library(dplyr)
library(knitr)
library(tidyverse)
library(kableExtra)
library(tidyr)
library(ggplot2)
library(gbm)
library(caret)
library(xgboost)
library(e1071)
library(class)
library(ROCR)
library(randomForest)
library(PRROC)
library(reshape2)
library(ggthemes)
library(lubridate)
library(pROC)
library(rpart)      
library(rpart.plot) 
library(tree)
```

# Introduction

This report uses a dataset of Kickstarter dating from 2018 available on Kaggle.  The dataset is loaded into R and the dataset structure is analysed.  Some trends can be observed and some conclusions can be derived from the visualization part. Then, some machine learning models are applied to estimate the accuracy of predicting the success or failure of a Kickstarter campaign based on some predicators.
The used dataset has been stored in Github.

## The dataset

The dataset in a CSV format is first of all loaded and then the dataset structure is looked at.  The datset has a size of 55MB with 15 columns and 378661 rows.  We can see here below a short view of what is contained in the dataset. 
```{r }
#loading the data from a local HD
setwd("~/projects/Capstone/Capstone")
data <- read_csv("ks-projects-201801.csv")

summary(data)

#dimensions of the dataset
dim(data)

#Information and column's headers
head(data, 5)
tail(data, 5)
```

## Data Cleansing

The dataset requires cleansing since some states are set as "undefined" which does not provide any information regarading the success of failure of a project, and this state does not follow the pledges having reached their goals.  We are removing a column that does not bring much information and removing any rows where the "undefined" state is set.  In the same way we are removing any state set as "successful" which does not have any backers.  This does not make sense.
We are adding a new column called "launched_year" which uses only the year in the launch column.
```{r , echo=FALSE}
#Everything looks okay so far. Now let's check to see if there are any N/A values that we have to clean up.
sapply(data, function(x) sum(is.na(x)))
#is.na(data$`usd pledged`)

#Looking at all the different state of a Kickstarter campaign. We can see that some **undefined state* are present, which requires fixing.
table(data$state)

#There appears to only be N/A values for *usd.pledged*. We actually don't need that column since we'll be using *usd_pledged_real* instead, so let's get rid of it and rename *usd_pledged_real* to *usd_pledged*. Likewise, we'll do the same with *usd_goal_real* and simply name it *usd_goal*.
data <- data[,-13]
colnames(data)[13] <- "usd_pledged"
colnames(data)[14] <- "usd_goal"

#Checking the data once more
head(data)

#Removing at the projects set as **successful** but having 0 backers, which is strange
data <- filter(data, backers != 0 | state != "successful")

#Number of **undefined** state 
sum(data$state=="undefined")

#Cleansing the **undefined* state from the dataset
data <- data %>% filter(state!="undefined")

#Addind a new column called **launched_year**
data$launched_year <- year(data$launched)
```

## Data Exploratory

We will look at the projects that are the most popular.  The dataset includes 2 columns, "main_category" and "category".  The former provides informtaion in which category a project falls and the latter gives a better insight of the category.  The plot here below whows the projects in function of main categories:

```{r , echo=FALSE}
cat.freq <- data %>%
  group_by(main_category) %>%
  summarize(count=n()) %>%
  arrange(desc(count))
#Ranking of the **main_category**
cat.freq

cat.freq$main_category <- factor(cat.freq$main_category, levels=cat.freq$main_category)


ggplot(cat.freq, aes(main_category, count, fill=count)) + geom_bar(stat="identity") + 
  ggtitle("Projects by Category") + xlab("Project Category") + ylab("Frequency") + 
  geom_text(aes(label=count), vjust=-0.5) + theme_economist() + 
  theme(plot.title=element_text(hjust=0.5), axis.title=element_text(size=12, face="bold"), 
        axis.text.x=element_text(size=12, angle=90), legend.position="null") + 
  scale_fill_gradient(low="skyblue1", high="royalblue4")

```

We can see that the most popular Kickstarter campaign falls under the category of "Film & Video" main category.  It would be good to get more insight of what this entails exactly. Looking at the projects in function of subcategory we can see, plot below, the "Product Design" is the most popular Kickstarter campaign subcategory.

```{r , echo=FALSE}
subcat.freq <- data %>%
  group_by(category) %>%
  summarize(count=n()) %>%
  arrange(desc(count))
#Ranking of the **category**
subcat.freq

subcat.freq$category <- factor(subcat.freq$category, levels=subcat.freq$category)

ggplot(head(subcat.freq, 10), aes(category, count, fill=count)) + geom_bar(stat="identity") + 
  ggtitle("Projects by Subcategory") + xlab("Project Subcategory") + ylab("Frequency") + 
  geom_text(aes(label=count), vjust=-0.5) + theme_economist() + 
  theme(plot.title=element_text(hjust=0.5), axis.title=element_text(size=12, face="bold"), 
        axis.text.x=element_text(size=12, angle=90), legend.position="null") + 
  scale_fill_gradient(low="skyblue1", high="royalblue4")

```

Althougt the "Product Design" is the most popular subcategory, we can view the 15 campaigns that are the most pledged:
```{r , echo=FALSE}
head(data[order(-data$usd_pledged), c(1,2,3,13)], 15)
```
We can see that that most of those most pledged projects fall under the "Product Design" category.

In the same way here below we can see the most popular projects being backed up:
```{r , echo=FALSE}
head(data[order(-data$backers), c(2,3,11)], 15)
```
We can see here that a few projects listed here are under the "Video Games" category.

We can now look at the project categories in function of the amount pledged.  This represents the categories requiring the most money:

```{r , echo=FALSE}
pledged.tot <- data %>%
  group_by(main_category) %>%
  summarize(total=sum(usd_pledged)) %>%
  arrange(desc(total))

pledged.tot$main_category <- factor(pledged.tot$main_category, levels=pledged.tot$main_category)

ggplot(pledged.tot, aes(main_category, total/1000000, fill=total)) + geom_bar(stat="identity") + 
  ggtitle("Total Amount Pledged by Category") + xlab("Project Category") + 
  ylab("Amount Pledged (USD millions)") + 
  geom_text(aes(label=paste0("$", round(total/1000000,1))), vjust=-0.5) + theme_economist() + 
  theme(plot.title=element_text(hjust=0.5), axis.title=element_text(size=12, face="bold"), 
        axis.text.x=element_text(size=12, angle=90), legend.position="null") + 
  scale_fill_gradient(low="skyblue1", high="royalblue4")
```

We can see that "Games", "Design" and "technology" are the categories that total the most revenues.  The projects pledged can be now visulaized per category using the boxplot.  From this graph, here below, it is possible to see that outliers exist as well as some displersion and skeweness in the data.

```{r , echo=FALSE}
 ggplot(data, aes(main_category, usd_pledged, fill=main_category)) + geom_boxplot() + 
  ggtitle("Amount Pledged vs. Project Category") + xlab("Project Category") + 
  ylab("Amount Pledged (USD)") + theme_economist()+ 
  theme(plot.title=element_text(size=15, face="bold", hjust=0.5), 
        axis.title=element_text(size=12, face="bold"), 
        axis.text.x=element_text(size=12, angle=90), legend.position="null") + 
  coord_cartesian(ylim=c(0,20000))
```

Projects in Design represent the biggest interquantile range followed by Games and technology.  Now it will be good to understand which categories are backed the most, in order of preference.  The graph below shows that projects falling under "Technology" are the most backed up.

```{r , echo=FALSE}
 pledged.avg <- data %>%
  group_by(main_category) %>%
  summarize(pledged=sum(usd_pledged), backers=sum(backers)) %>%
  mutate(avg=pledged/backers) %>%
  arrange(desc(avg))

pledged.avg$main_category <- factor(pledged.avg$main_category, levels=pledged.avg$main_category)

ggplot(pledged.avg, aes(main_category, avg, fill=avg)) + geom_bar(stat="identity") + 
  ggtitle("Average Amount Pledged per Backer") + xlab("Project Category") + 
  ylab("Amount Pledged (USD)") + 
  geom_text(aes(label=paste0("$", round(avg,2))), vjust=-0.5) + theme_economist() + 
  theme(plot.title=element_text(hjust=0.5), axis.title=element_text(size=12, face="bold"), 
        axis.text.x=element_text(size=12, angle=90), legend.position="null") + 
  scale_fill_gradient(low="skyblue1", high="royalblue4")
```

We can now look at the status of the different projects run in Kickstarter, see graph below.  The majority of projects have failed, the successful projects are about 67% of the proportion of failed projects.

```{r , echo=FALSE}
 state.freq <- data %>%
  group_by(state) %>%
  summarize(count=n()) %>%
  arrange(desc(count))

state.freq$state <- factor(state.freq$state, levels=state.freq$state)

ggplot(state.freq, aes(state, count, fill=count)) + geom_bar(stat="identity") + 
  ggtitle("Projects by Status") + xlab("Project Status") + ylab("Frequency") + 
  geom_text(aes(label=count), vjust=-0.5) + theme_economist() + 
  theme(plot.title=element_text(hjust=0.5), axis.title=element_text(size=12, face="bold"), 
        axis.text.x=element_text(size=12), legend.position="null") + 
  scale_fill_gradient(low="skyblue1", high="royalblue4")
```

Since there are different status existing in this dataset, we can see the porportion of completed projects versus the ones that have been stopped before.

```{r , echo=FALSE}
state.grp <- data %>%
  filter(state!="undefined") %>%
  mutate(grp=ifelse(state %in% c("successful", "failed"), "complete", "incomplete")) %>%
  group_by(grp, state) %>%
  summarize(count=n()) %>%
  mutate(pct=count/sum(count)) %>%
  arrange(grp, desc(state))

state.grp$state <- factor(state.grp$state, levels=state.grp$state)

ggplot(state.grp, aes(grp, pct, fill=state)) + geom_bar(stat="identity") + 
  ggtitle("Project Status by Completion") + xlab("Project Completion") + ylab("Percentage") + 
  scale_x_discrete(labels=c("Complete", "Incomplete")) + 
  scale_y_continuous(labels=scales::percent) + 
  scale_fill_brewer(name="Project Status", 
                    labels=c("Successful", "Failed", "Suspended", "Live", "Cancelled"), 
                    palette="Set1") + 
  geom_text(aes(label=paste0(round(pct*100,1),"%")), position=position_stack(vjust=0.5), 
            colour="white", size=5) + theme_economist() + 
  theme(plot.title=element_text(hjust=0.5), axis.title=element_text(size=12, face="bold"), 
        axis.text.x=element_text(size=12), legend.position="bottom", 
        legend.title=element_text(size=12, face="bold"))
```

This graph is much clearer in terms of the success rate of a porject in Kickstarter irrespective of the category the project falls into.  Only ~40% of the projects are successful and ~90% of the porjects were cancelled.  We can now see the porject success ratio per category as well as their numbers.  Projects in categories such as Dance, Theater and Comics have a success rate of 60% or above, however their numbers are much lower than other projects.

```{r , echo=FALSE}
state.pct <- data %>%
  filter(state %in% c("successful", "failed")) %>%
  group_by(main_category, state) %>%
  summarize(count=n()) %>%
  mutate(pct=count/sum(count)) %>%
  arrange(desc(state), pct)

state.pct$main_category <- factor(state.pct$main_category, 
                                  levels=state.pct$main_category[1:(nrow(state.pct)/2)])

cat1 <- ggplot(state.pct, aes(main_category, pct, fill=state)) + geom_bar(stat="identity") + 
  ggtitle("Success vs. Failure Rate by Project Category") + 
  xlab("Project Category") + ylab("Percentage") + scale_y_continuous(labels=scales::percent) + 
  scale_fill_discrete(name="Project Status", breaks=c("successful", "failed"),
                      labels=c("Success", "Failure")) + 
  geom_text(aes(label=paste0(round(pct*100,1),"%")), position=position_stack(vjust=0.5), 
            colour="white", size=3) + theme_economist() + 
  theme(plot.title=element_text(hjust=0.5), axis.title=element_text(size=12, face="bold"), 
        axis.text.x=element_text(size=12), legend.position="bottom", 
        legend.title=element_text(size=12, face="bold")) + coord_flip()

cat2 <- ggplot(state.pct, aes(main_category, count, fill=state)) + geom_bar(stat="identity") + 
  ggtitle("Success vs. Failure Rate by Project Category") + 
  xlab("Project Category") + ylab("Number of Projects") + scale_y_continuous(labels=scales::comma) + 
  scale_fill_discrete(name="Project Status", breaks=c("successful", "failed"),
                      labels=c("Success", "Failed")) + 
  geom_text(aes(label=paste0(round(count,1),"")), position=position_stack(vjust=0.5), 
            colour="white", size=3) + theme_economist() + 
  theme(plot.title=element_text(hjust=0.5), axis.title=element_text(size=12, face="bold"), 
        axis.text.x=element_text(size=12), legend.position="bottom", 
        legend.title=element_text(size=12, face="bold")) + coord_flip()

gridExtra::grid.arrange(cat1, cat2, ncol = 2)
```


Although Kickstarter rules for the maximum project length is 60 days, they recommend to set the length of time for 30 days.  From our dataset we can see that in geenral any project lasting more than 30 days have a lower sucess rate from the ones lasting between 5 to 30 days. 

```{r , echo=FALSE}
data$length <- interval(ymd_hms(data$launched), ymd(data$deadline)) %/% days(1)

length.pct <- data %>%
  filter(state %in% c("successful", "failed"), length <= 61) %>%
  group_by(length, state) %>%
  summarize(count=n()) %>%
  mutate(pct=count/sum(count))

ggplot(length.pct[length.pct$state=="successful",], aes(length, pct)) + 
  geom_point(colour="royalblue4", size=2.5) + ggtitle("Success Rate vs. Project Length") + 
  xlab("Project Length (Days)") + ylab("Success Rate (%)") + 
  scale_x_continuous(breaks=c(0,10,20,30,40,50,60)) + geom_vline(xintercept=30, colour="red") + 
  theme_economist() + 
  theme(plot.title=element_text(hjust=0.5), axis.title=element_text(size=12, face="bold"))
```

Projects also varies in time and the graph, here below, shows the success rate of the project over time.  2014 and 2015 have been the years where the most porjects were launched however looking at the sucess ratio, we can see that the failure is quite constant over the years.

```{r , echo=FALSE}
year.freq <- data %>%
  filter(year(launched)!="1970", state %in% c("successful", "failed")) %>%
  group_by(year=year(launched)) %>%
  summarize(count=n())

plot1 <- ggplot(year.freq, aes(year, count, fill=count)) + geom_bar(stat="identity") + 
  ggtitle("Number of Projects by Launch Year") + xlab("Year") + ylab("Frequency") + 
  scale_x_discrete(limits=c(2009:2018)) + 
  geom_text(aes(label=paste0(count)), vjust=-0.5) + theme_economist() + 
  theme(plot.title=element_text(hjust=0.5), axis.title=element_text(size=12, face="bold"), 
        axis.text.x=element_text(size=12), legend.position="null") + 
  scale_fill_gradient(low="skyblue1", high="royalblue4")

state.pct2 <- data %>%
  filter(year(launched)!="1970", state %in% c("successful", "failed")) %>%
  group_by(year=year(launched), state) %>%
  summarize(count=n()) %>%
  mutate(pct=count/sum(count)) %>%
  arrange(desc(state))

plot2 <- ggplot(state.pct2, aes(year, count, fill=state)) + geom_bar(stat="identity") + 
  ggtitle("Success vs. Failure Rate by Year Launched") + 
  xlab("Year") + ylab("Frequency") + scale_x_discrete(limits=c(2009:2018)) + 
  scale_y_continuous() + 
  scale_fill_discrete(name="Project Status", breaks=c("successful", "failed"),
                      labels=c("Success", "Failed")) + 
  geom_text(aes(label=paste0(count,"")), position=position_stack(vjust=0.5), 
            colour="white", size=3) + theme_economist() + 
  theme(plot.title=element_text(hjust=0.5), axis.title=element_text(size=12, face="bold"), 
        axis.text.x=element_text(size=12), legend.position="bottom", 
        legend.title=element_text(size=12, face="bold"))

gridExtra::grid.arrange(plot1, plot2, ncol = 2)
```

Projects vary also per country and currency.  The majority of projects are coming out from the USA followed by Great Britain and Canada.  In terms of the currency the most used currency is the US dollar, then quite far behind is the British pounds and then the Euro.  The success rate is around 40% for either projects launched in the US and Great Britain or in US dollar and British pounds.  Projects launched in Euros have a success rate of only 27% though.

```{r , echo=FALSE}
countries.freq <- data %>%
  filter(country!='N,0"', state %in% c("successful", "failed")) %>%
  group_by(country, state) %>%
  summarize(count=n())%>%
  mutate(pct2=count/sum(count)) %>%
  arrange(desc(count), pct2)


pp1 <- ggplot(head(countries.freq,10), aes(country,count, fill=state)) + geom_bar(stat="identity") + 
  ggtitle("Projects by Country") + 
  xlab("Country") + ylab("Frequency") + scale_y_continuous(labels=scales::comma)+ 
  scale_fill_discrete(name="Project Status", breaks=c("successful", "failed"),
                      labels=c("Success", "Failed")) + 
  geom_text(aes(label=paste0(round(pct2*100,1),"%")), position=position_stack(vjust=0.5), 
            colour="black", size=5) + theme_economist() + 
  theme(plot.title=element_text(hjust=0.5), axis.title=element_text(size=12, face="bold"), 
        axis.text.x=element_text(size=12), legend.position="bottom", 
        legend.title=element_text(size=12, face="bold"))


currency.freq <- data %>%
  filter(country!='N,0"', state %in% c("successful", "failed")) %>%
  group_by(currency, state) %>%
  summarize(count=n())%>%
  mutate(pct3=count/sum(count)) %>%
  arrange(desc(count), pct3)


pp2 <- ggplot(head(currency.freq,10), aes(currency,count, fill=state)) + geom_bar(stat="identity") + 
  ggtitle("Projects by Currency") + 
  xlab("Currency") + ylab("Frequency") + scale_y_continuous(labels=scales::comma)+ 
  scale_fill_discrete(name="Project Status", breaks=c("successful", "failed"),
                      labels=c("Successful", "Failed")) + 
  geom_text(aes(label=paste0(round(pct3*100,1),"%")), position=position_stack(vjust=0.5), 
            colour="black", size=5) + theme_economist() + 
  theme(plot.title=element_text(hjust=0.5), axis.title=element_text(size=12, face="bold"), 
        axis.text.x=element_text(size=12), legend.position="bottom", 
        legend.title=element_text(size=12, face="bold"))

gridExtra::grid.arrange(pp1, pp2, ncol = 2)
```

# Data correlation

Now that we have view different dataset, it is possible to see whether some data have a high correlation between them of now.  THis can be done graphically but also tabularly.

```{r , echo=FALSE}
frequency.goal <- data %>%
  filter(goal!="0", state %in% c("successful", "failed")) %>%
  group_by(goal, state) 
#backers in function of usd pledged
ggplot(frequency.goal, aes(log(backers),log(usd_pledged), color=state)) + 
  geom_point(position="identity") + theme_economist() +  
  ggtitle("Backers in function of pledges") + xlab("log(Backers)") + 
  ylab("USD Pledged")

#Goals in function of usd pledged
ggplot(frequency.goal, aes(log(usd_goal),log(usd_pledged), color=state)) + 
  geom_point(position="identity") + theme_economist() +  
  ggtitle("Goals in function of Pledges") + xlab("log(USD Goals)") + 
  ylab("USD Pledged")

#Goals in function of backers
ggplot(frequency.goal, aes(log(backers),log(usd_goal), color=state)) + 
  geom_point(position="identity") + theme_economist() +  
  ggtitle("Backers in function of Goals") + xlab("log(Backers)") + 
  ylab("USD Pledged")


#Pledge's length in function of backers
ggplot(frequency.goal, aes((length),log(usd_goal), color=state)) + 
  geom_point(position="identity") + theme_economist() +  
  ggtitle("Pledge's length in function of USD Goals") + xlab("length") + 
  ylab("USD Pledged")


#Pledge's length in function of backers
ggplot(frequency.goal, aes(year(launched), fill=state)) + 
  geom_bar() + theme_economist() +  facet_wrap( ~ main_category) +
  ggtitle("Pledges in function of years") + xlab("Category") + 
  ylab("USD Pledged")

```

As for the graphs we can see that the best correlation is obtained between pledge and backers.

```{r , echo=FALSE}
cor(data[,c(11,13:15)])
```


# Modelling part

We saw that some correlations exist in the dataset, we are now going to use some models to fit a subset of the dataset. Here we use 10% of the dataset for the training set.  


```{r , echo=FALSE}
#select the features we believe have an impact on project success or failure
subset1 <- data %>% select(state,  main_category, usd_goal, country, backers, usd_pledged, length, launched_year)

#filter the state variable to just successful or failed projects.  (Other states exist like live, cancelled, etc.) 
subset1 <- subset1 %>% filter(., state=="successful" | state =="failed")

#Factorize categorical varibles:
subset1$state <- as.factor(subset1$state)
subset1$main_category <- as.factor(subset1$main_category)
subset1$country <- as.factor(subset1$country)
subset1$launched <- as.factor(subset1$launched_year)


#omit NA values
subset1 = na.omit(subset1)

#Binarize state variables
#subset1$state <- ifelse(subset1$state=="successful", 1, 0)

#Creating partition for test and training datasets
set.seed(77777777, sample.kind="Rounding")
test_index <- createDataPartition(y = subset1$state, times = 2, p = 0.1, list = FALSE)
trainset <- subset1[-test_index,]
testset <- subset1[test_index,]
```

Some models such as K-Neareast Neighbor (KNN), Random Forest (RF), New View (NV) and Support Vector Machine (SVM) take too long to find convergence and we are just using 2 that provide relatively quickly some outcomes.  Those models are Logistic Regression (LDA) and Classification And Regression Trees (CART).
```{r , include=FALSE, echo=FALSE}
set.seed(11)
fit.lda <- train(state~., data=trainset, method="lda")
# CART
set.seed(111)
fit.cart <- train(state~., data=trainset, method="rpart")

```
```{r , echo=FALSE}
# summarize accuracy of used models
results <- resamples(list(lda=fit.lda, cart=fit.cart))
summary(results)
```

We can see the results of both LDA and CART training models on the training dataset.  We can look at the most influencial predictors in this training set using the tree methodology, as see below.  The most influencial predictors:
- backers 
- usd goals
- usd pledged

We then apply the model to the rest of the dataset to look at the accuraacy of our model.  We can see that a good accuracy is obtained, with an area under the curve of above 0.95. 

```{r , echo=FALSE}
#Tree model selection view - showing the most significant predictors
tree1 <- tree(state ~ . , data = trainset)
summary(tree1)
plot(tree1)
text(tree1)
prediction <- predict(tree1, testset)
validation <- data.frame( v_state = testset$state, pred_state = prediction)
validation$check <- ifelse(validation$pred_state.successful < 0.5, 0, 1)

table(validation$v_state, validation$check)

auc(validation$v_state, validation$check)
```







